plyranges: a grammar for transforming genomics data

### 2018-05-09 paper.Rmd
some comments on first example

@@

@@

>>>>

[ML: please explain why we are doing this. Something like: we need to
     get the range for chromosome 10, so that we can use it as a
     filter when reading. The first time I read this, I was not sure what
     'annotation information' and 'gather' meant here. Why say
     "annotation information" when the API uses "genome information"?]

@@

[ML: getting the genome info does not look automatic, because we are calling
	`set_genome_info()`; is that supposed to be here?]

@@

[ML: I think the above text could do a better job of describing what
	`reduce_ranges()` does generally. You could say something like, after
	filtering for regions with a score greater than 8, we can reduce the
	individual runs to ranges representing the islands of coverage.]
